\begin{rSection}{Publications}

Find a more complete listing with associated materials here: \url{https://lalejini.com/publications/}.

Google scholar profile: \url{https://bit.ly/lalejini-scholar}

* = denotes undergraduate mentee co-authors

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% JOURNAL
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\underline{\large {\bf Peer-reviewed journal}}

\begin{itemize}
  \item Emily Dolson, \textbf{Alexander Lalejini}, Steven Jorgensen$^{*}$, and Charles Ofria. (2020).
  Interpreting the Tape of Life: Ancestry-based metrics and visualizations provide insights and intuition about evolutionary dynamics.
  Artificial Life. MIT Press. DOI: 10.1162/artl\_a\_00313
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CONFERENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\underline{\large {\bf Peer-reviewed conference}}

\begin{itemize}

\item Clifford Bohm, \textbf{Alexander Lalejini}, Jory Schossau, and Charles Ofria. (2019).
MABE 2.0: an introduction to MABE and a road map for the future of MABE development.
In Proceedings of the Genetic and Evolutionary Computation Conference Companion (GECCO ‘19), Manuel López-Ibáñez (Ed.). ACM, New York, NY, USA, 1349-1356.
\url{https://doi.org/10.1145/3319619.3326825}

\item Jose Guadalupe Hernandez, \textbf{Alexander Lalejini}, Emily Dolson, and Charles Ofria. (2019).
Random subsampling improves performance in lexicase selection.
In Proceedings of the Genetic and Evolutionary Computation Conference Companion (GECCO ‘19), Manuel López-Ibáñez (Ed.). ACM, New York, NY, USA, 2028-2031.
\url{https://doi.org/10.1145/3319619.3326900}

\item \textbf{Alexander Lalejini}, Emily Dolson, Clifford Bohm, Austin J. Ferguson, David P. Parsons, Penelope Faulkner Rainford, Paul Richmond, and Charles Ofria (2019).
Data Standards for Artificial Life Software.
The 2019 Conference on Artificial Life, 507–514.
\url{https://doi.org/10.1162/isal_a_00213}

\item \textbf{Alexander Lalejini} and Charles Ofria. (2018).
Evolving event-driven programs with SignalGP.
In Proceedings of the 2018 Genetic and Evolutionary Computation Conference (GECCO). pp. 1135-1142.
DOI: 10.1145/3205455.3205523. ACM.

\item Emily Dolson, \textbf{Alexander Lalejini}, Steven Jorgensen$^{*}$, and Charles Ofria. (2018).
Quantifying the tape of life: Ancestry-based metrics provide insights and intuition about evolutionary dynamics.
In Proceedings of the 2018 Conference on Artificial Life (ALIFE).
Edited by Takashi Ikegami, Nathaniel Virgo, Olaf Witkowski, Mizuki Oka, Reiji Suzuki, and Hiroyuki Iizuka. pp. 75-82.
DOI: 10.1162/isal\_a\_00020. MIT Press.

\item \textbf{Alexander Lalejini}, Michael J. Wiser, and Charles Ofria. (2017).
Gene duplications drive the evolution of complex traits and regulation.
In Proceedings of the 14th European Conference on Artificial Life (ECAL) 2017.
Edited by Carole Knibbe, Guillaume Beslon, David Parsons, Dusan Misevic, Jonathan Rouzaud-Cornabas, Nicolas Bredèche, Salima Hassas, Olivier Simonin, and Hédi Soula. Vol 14. pp. 257-264.
DOI: 10.7551/ecal\_a\_045. MIT Press.

\item \textbf{Alexander Lalejini} and Charles Ofria. (2016).
The evolutionary origins of phenotypic plasticity.
In Artificial Life XV: Proceedings of the Fifteenth International Conference on the Synthesis and Simulation of Living Systems (ALIFE).
Edited by Carlos Gershenson, Tom Froese, Jesus M. Siqueiros, Wendy Aguilar, Eduardo J. Izquierdo and Hiroki Sayama. Vol 14. pp. 372-379.
DOI: 10.7551/978-0-262-33936-0-ch063. MIT Press.

\item Christopher R. Hudson, \textbf{Alexander Lalejini}, Brandon Odom, Daniel W. Carruth, Cindy L. Bethel, Phillip J. Durst, and Christopher Goodin. (2015).
ANVEL-ROS: The integration of the robot operating system with a high-fidelity simulator.
In Proceedings of the 2015 Ground Vehicle Systems Engineering and Technology Symposium (GVSETS). p. 378.

\item \textbf{Alexander Lalejini}, Dexter Duckworth, Richard Sween, Cindy L. Bethel, and Daniel W. Carruth. (2014).
Evaluation of supervisory control interfaces for mobile robot integration with tactical teams.
In Proceedings of 2014 IEEE Workshop on Advanced Robotics and Its Social Impacts (ARSO). pp 1-6.
DOI: 10.1109/ARSO.2014.7020971. IEEE.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\underline{\large {\bf Peer-reviewed abstracts}}

These are short (usually 2-page) summaries of research recently published or to be published elsewhere.
They are usually held to slightly lower peer-review standards than full papers submitted to the same venue and are often presented as posters rather than talks.

\begin{itemize}

\item \textbf{Alexander Lalejini} and Charles Ofria. (2019).
Tag-accessed memory for genetic programming.
In Proceedings of the Genetic and Evolutionary Computation Conference Companion (GECCO ‘19), Manuel López-Ibáñez (Ed.).
ACM, New York, NY, USA, 346-347.
DOI: \url{https://doi.org/10.1145/3319619.3321892}

\item \textbf{Alexander Lalejini} and Charles Ofria. (2018).
Evolving reactive agents with SignalGP.
In Proceedings of the 2018 Conference on Artificial Life (ALIFE). Edited by Takashi Ikegami, Nathaniel Virgo, Olaf Witkowski, Mizuki Oka, Reiji Suzuki, and Hiroyuki Iizuka. pp. 368-369.
DOI: 10.1162/isal\_a\_00069. MIT Press.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BOOK CHAPTERS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\underline{\large {\bf Book chapters}}

\begin{itemize}

\item Austin J. Ferguson, Jose G. Hernandez, Daniel Junghans$^{*}$, \textbf{Alexander Lalejini}, Emily Dolson, Charles Ofria (2020).
Characterizing the Effects of Random Subsampling on Lexicase Selection.
In: Banzhaf W., Goodman E., Sheneman L., Trujillo L., Worzel B. (eds) Genetic Programming Theory and Practice XVII.
Genetic and Evolutionary Computation. Springer, Cham

\item \textbf{Alexander Lalejini} and Charles Ofria (2019).
What Else Is in an Evolved Name? Exploring Evolvable Specificity with SignalGP.
In Banzhaf W., Spector L., Sheneman L. (eds) Genetic Programming Theory and Practice XVI.
Genetic and Evolutionary Computation. Springer, Cham

\item Emily Dolson, \textbf{Alexander Lalejini}, and Charles Ofria. (2019).
Exploring Genetic Programming Systems with MAP-Elites.
In Banzhaf W., Spector L., Sheneman L. (eds) Genetic Programming Theory and Practice XVI. Genetic and Evolutionary Computation. Springer, Cham

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MISC
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\underline{\large {\bf Miscellaneous}}

Miscellaneous scientific publications that are not peer reviewed.

\begin{itemize}

\item Nadine Strasser, \textbf{Alexander Lalejini}, and Charles Ofria (2020).
Detecting the genetic signature of mutualisms from lineages.
The 2020 Workshop on Symbiosis in Artificial Life at the 2020 Conference on Artificial Life.

\item Lauren Gillespie, Emily Dolson, \textbf{Alexander Lalejini}, and Charles Ofria (2018).
Changing Environments Drive the Separation of Genes and Increased Evolvability in NK-Inspired Landscapes.
Late breaking abstract at The 2018 Conference on Artificial Life.

\end{itemize}

\end{rSection}