\begin{rSection}{Service \& Outreach}

Conference chair (elected), Emerging Researchers in Artificial Life
\hfill Fall 2019 - Fall 2020 \\
\tab Led conference activities for junior researchers at the 2020 Artificial Life conference.

Mentor, Workshop for Avida-ED Software Development (WAVES)
\hfill Summer 2020 \\
\tab Mentored two workshop participants over a 10 week period. \\
\tab Mentees developed open-source software benefitting the Avida-ED software platform.

Mentor, MSU Summer Research Opportunities Program (SROP)
\hfill 2016 - 2019 \\
\tab SROP supports underrepresented undergraduates interested in graduate study and research careers. \\
\tab As a mentor, I work closely with undergraduate mentees to develop and carry out summer research.

Co-instructor, `Making a Game of It' summer camp for high school students
\hfill Summer 2019 \\
\tab Michigan State University College of Engineering Summer Programs, East Lansing, MI \\
\tab Prepared and co-instructed a one week intensive introduction to Python and video game design.

Volunteer, BEACON Outreach Activities
\hfill 2015 - present \\
\tab Teach students about evolution biology at elementary school science nights. \\
\tab Help run the BEACON education booth at the annual MSU Science Festival.

Volunteer, Poolside judge for the National SeaPerch Challenge \hfill May 2014

Journal and conference reviews
\vspace{-0.5em}
\begin{itemize}[noitemsep]
  \item Artificial Life Conference (ALIFE): 2016 - 2020
  \item Genetic and Evolutionary Computation Conference (GECCO): 2018
  \item European Conference on Artificial Life (ECAL): 2017
\end{itemize}

\end{rSection}